\documentclass[helvetica]{seminar} 
\input{xy}
\xyoption{all}
\usepackage{graphicx} 
\usepackage{slidesec} 
% \usepackage{url}
\usepackage{hyperref}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{color}
\usepackage[normalem]{ulem}  

\def\dash---{\unskip\kern.16667em---\penalty\exhyphenpenalty\hskip.16667em\ignorespaces}
\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

% to fix problems making landscape seminar pdfs
% Letter...
\pdfpagewidth=11truein
\pdfpageheight=8.5truein
\pdfhorigin=1truein     % default value(?), but doesn't work without
\pdfvorigin=1truein     % default value(?), but doesn't work without
% A4
%\pdfpagewidth=297truemm % your milage may vary....
%\pdfpageheight=210truemm
%\pdfhorigin=1truein     % default value(?), but doesn't work without
%\pdfvorigin=1truein     % default value(?), but doesn't work without


\renewcommand{\familydefault}{\sfdefault}  
 
\input{seminar.bug} 
\input{seminar.bg2} % See the Seminar bugs list 
 
\slideframe{none} 
 
 
\usepackage{fancyhdr} 
 
% Headers and footers personalization using the `fancyhdr' package 
\fancyhf{} % Clear all fields 
\renewcommand{\headrulewidth}{0mm} 
\renewcommand{\footrulewidth}{0.1mm} 
 
\fancyfoot[L]{\tiny IETF 99} 
\fancyfoot[C]{\tiny IASA 2.0}
\fancyfoot[R]{\tiny \theslide} 
 
 
% To center horizontally the headers and footers (see seminar.bug) 
\renewcommand{\headwidth}{\textwidth} 

% To adjust the frame length to the header and footer ones 
\autoslidemarginstrue 
\pagestyle{fancy} 
 

\newcommand{\heading}[1]{% 
  \begin{center} 
    \large\bf 
    #1 
  \end{center} 
  \vspace{.4 in}} 



\begin{document}

\begin{slide}
\begin{center}
\vspace{.5 in}
\LARGE{{\bf}IASA 2.0 Design Team Update\\{\small \verb^draft-haberman-iasa20dt-recs-00^}}\\
\vspace{.2in}
\large{
\begin{tabular}{ c c c }
B. Haberman & J. Arkko & L. Daigle \\
J. Livingood & J.L. Hall & E. Rescorla 
\end{tabular}
}
\end{center}
\end{slide}

\centerslidesfalse 

\begin{slide}
\heading{Outline}

%\vspace{-8ex}         %for long lists
\begin{itemize}
\item Status and what feedback we're looking for
\item High-level description of IASA 2.0 options
\item Overview of feedback received so far
\end{itemize}

\end{slide}


\begin{slide}

\heading{Status and desired feedback}

{\footnotesize
\begin{itemize}
\item We do not yet have fully specified options for you
\item And we have only started the analysis of the differences between options
\item But we think we have an understanding of what options there are
\item Looking for feedback on:
  \begin{itemize}
  \item Whether we are missing top-level options or other aspects
  \item What factors should be considered when comparing the options
  \item Missing options or comparison factors would be most useful at this point, but all feedback is welcome!
  \item (This meeting probably shouldn't be about "let choose option D")
  \end{itemize}
\item Very thankful for feedback already received! (More on that later)
\end{itemize}
}
\end{slide}

\begin{slide}

\heading{Areas of Possible Reorganisation}
\begin{itemize}
\item Oversight
\item Staffing
\item Organisational structure
\item Relationship to ISOC
\end{itemize}
\end{slide}

\begin{slide}

\heading{IASA 2.0 Options the DT is considering}

\begin{itemize}
\item IASA++
\item ISOC Subsidiary
\item Independent Organization
\end{itemize}

\end{slide}

\begin{slide}

\heading{IASA++}

\begin{itemize}
\item IETF and ISOC maintain current structural relationship
\item ISOC maintains funds and contracting authority on behalf of the IETF
\item All IASA staff are ISOC employees
\item IETF and ISOC will make improvements to the relationship to enhance functionality of the IETF
\end{itemize}

\end{slide}

\begin{slide}

\heading{ISOC Subsidiary}

\begin{itemize}
\item Create new ISOC subsidiary as new legal home of the IETF
\item Subsidiary maintains its own:
{\footnotesize
\begin{itemize}
\item By-laws
\item Bank account
\item Charter
\item Board
\item Staff
\item ...
\end{itemize}
}
\item Potentially heavy reliance on contractors for administrative tasks
\item Could eliminate IAOC and replace it with Board of Directors
\item Administrative staff holds administrative decision-making authority (with oversight)
\end{itemize}

\end{slide}

\begin{slide}

\heading{Independent Organization}

\begin{itemize}
\item Create a new non-profit (e.g., IETForg) as new legal home of the IETF
\item IETForg maintains its own:
{\footnotesize
\begin{itemize}
\item By-laws
\item Bank account
\item Charter
\item Board
\item Staff
\item ...
\end{itemize}
}
\item Potentially heavy reliance on contractors for administrative tasks
\item Administrative staff notionally responsible for administration, fundraising, communications, and personnel
\end{itemize}

\end{slide}

\begin{slide}

\heading{Open questions with the options}

\begin{itemize}
\item Transfer of intellectual property
\item Transfer of contracts
\item Administrative oversight model
\item Transfer of funds
\item Structure of community involvement
\end{itemize}

\end{slide}

\begin{slide}

\heading{Overview of feedback so far}

\begin{itemize}
\item General document feedback
\item Feeback on options
\item IAOC strategic vs. operational
\item Other feedback (transparency, IAOC selection, fundraising, etc.)
\end{itemize}

\end{slide}


\begin{slide}

\heading{General document feedback}

\vspace{-8ex}         %for long lists

\begin{itemize}
\item Stephen: we've only focused most on the legal separation issue.
\item Stephen: Did not find Section 6 clear or convincing.
\item Stephen: would be good for the document to write down what is
  working now that we need to be careful not to break (e.g., AMS staff
  today, lack of membership)
\item Brian Carpenter: Problem statement in Section 3 is insufficient;
  need a consensus version of problem analysis.
\item Brian Carpenter: need to add a goal to define how volunteer
  contributions to the tasks interface to staff and contractors, and
  specifically how volunteer effort is directed and managed.
\item Brian Carpenter: We need to understand the conditions and the
  dynamics that led to the IAOC becoming effectively an executive
  committee rather than the oversight committee intended.
\item Brian Carpenter: a couple of embedded perception issues in the
  document that are difficult to understand:
  \begin{itemize}
  \item Perception of a lack of clarity about budget and money flow
    [which IMHO are perfectly clear from the published data, except
      for hidden staff costs].
  \item Perception of confusion about alignment between ISOC and IETF
    on policy and standards matters [which IMHO has been clear since
      1992 and has never changed].
  \end{itemize}
\end{itemize}

\end{slide}


\begin{slide}

\heading{Feeback on options}

%\vspace{-8ex}         %for long lists
\begin{itemize}
\item Stephen: it may be impossible to come to consensus on whether or
  not IETF should become an incorporated entity.
\item Ted: clarity on incorporation won't help us solve oversight
  miscalibration.
\item (offlist anon): we need to be careful not to mess with the
  org-pir-isoc-ietf pipe.
\item Bob Hinden: overisght that the draft does not discuss financial
  implications of each option
\item Bob Hinden: IETF Trust should be kept out of all of this; it is
  working and changing it risks effects like ICANN reconsidering
  having moved IANA trademarks and domain there.
\end{itemize}

\end{slide}


\begin{slide}

\heading{IAOC strategic vs. operational}

\vspace{-8ex}         %for long lists
\begin{itemize}
\item Ted: Oversight exercised by IAOC may not be appropriate
  (operational vs. strategic), but an independent design axis.
  \begin{itemize}
  \item skeptical that the IAOC could not suddenly revert to a more
    strategic approach now; many processes and committees are built
    around the current way of working.
  \end{itemize}
\item (offlist anon): skeptical of our ability to put in place a
  strategic management component as we haven’t done well in the past.
\item Matt Ford: natural for us to get operational; will need to
  design mechanisms that disincentivize these tendencies.
\item Brian Carpenter: missing bullet in 5.2: Whether the operational
  subcommittees (+volunteers) report to staff or oversight function.
\item Brian Carpenter: the ``Directors of x'' added by DT is arguably
  overdesign, should be ED that decides structure.
\end{itemize}

\end{slide}


\begin{slide}

\heading{Other feedback}

%\vspace{-8ex}         %for long lists

\begin{itemize}
\item IASA Transparency:
  \begin{itemize}
  \item Jordi: need to specify very clearly what is and is not open to
    the community.
  \item Stephen: would prefer a “default open” rule with an amendable
    list of exclusions.
  \end{itemize}
\item Selection of members of IASA committees
  \begin{itemize}
  \item Jordi: unlike the Nomcom process, IASA committees have a
    bootstrapped membership; should be more formal.
  \item Bob Hinden: Unless we can understand how to fix the difficulty
    of NomCom finding qualified volunteers for the IAOC, how is it
    going to fill positions on a Board of Directors?
  \end{itemize}
\item IAOC responses to the community
  \begin{itemize}
  \item Jordi: IAOC should have a more formal flow for responding to
    community input with deadlines.
  \end{itemize}
\item Fundraising:
  \begin{itemize}
  \item Bob Hinden: fund raising problem is not going to be fixed by
    adding a Director of Fundraising; the problems are more structural
    and caused by changes in the industry.
  \end{itemize}
\item Staff management:
  \begin{itemize}
  \item Bob Hinden: IETF is not very good about is managing staff; If
    we are going to have more staff, then this needs to be dealt with
    (writing performance reviews, setting appropriate goals, fairly
    judging their performance, replacing them as needed)
  \end{itemize}
\end{itemize}

\end{slide}



\end{document} 

                
